---
title: "ChrisWoodard6306wk4homework"
author: "cw"
date: "June 5, 2016"
output: html_document
keep_md: TRUE
---

#Week/Unit 4 - Bootstrap code to illustrate Central Limit Theorem

##Normal Distribution with two (2) different samples sizes

##Exponential Distribution with two (2) different sample sizes

###Normal Distribution n=30 (Sample size 1 of 2)
```{r, normal distribution 30, echo=TRUE}
x <- rnorm(30)
R <- 1000
bootmean <- numeric(R)
for (i in 1:R){
  bootsample <- sample(x, size=length(x), replace=TRUE)
  bootmean[i] <- mean(bootsample)}
mean(bootmean)
sd(bootmean)
hist(bootmean)
```

###Normal Distribution n=100 (Sample Size 2 of 2)
```{r, normal distribution 100, echo=TRUE}
x <- rnorm(100)
R <- 1000
bootmean <- numeric(R)
for (i in 1:R){
  bootsample <- sample(x, size=length(x), replace=TRUE)
  bootmean[i] <- mean(bootsample)}
mean(bootmean)
sd(bootmean)
hist(bootmean)
```

###Exponential Distribution n=30 (Sample Size 1 of 2)
```{r, expontential distribution 30, echo=TRUE}
x <- rexp(30)
R <- 1000
bootmean <- numeric(R)
for (i in 1:R){
  bootsample <- sample(x, size=length(x), replace=TRUE)
  bootmean[i] <- mean(bootsample)}
mean(bootmean)
sd(bootmean)
hist(bootmean)
```


###Exponential Distribution n=100 (Sample Size 2 of 2)
```{r, exponential distribution 100, echo=TRUE}
x <- rexp(100)
R <- 1000
bootmean <- numeric(R)
for (i in 1:R){
  bootsample <- sample(x, size=length(x), replace=TRUE)
  bootmean[i] <- mean(bootsample)}
mean(bootmean)
sd(bootmean)
```

##Comments:
The Central Limit Theorum states that the distribution of sample means will approach a "normal" bell curve shape as the sample size increases.  Also, as the sample size increases, the variance between means decreases (as you can see illustrated above)
The bootstrap function produces random simulations to a specified number (It was 1000 in all of the runs above) with a specified number of samples (n=30 and 1000).  Simulations were bootstrapped to be random normal distribution and random exponential distribution.